Lifting CDCL to Numerical Domains

### 2016-10-07 contributions.tex
decision

\section{Contributions}\label{contribution}
The goal of this paper is to instantiate ACDCL with 
different relational and non-relational numerical abstract 
domains and evaluate the performance of our solver with 
propositional-level solvers. Experimental evaluation on different
benchmarks shows that ACDCL is able to suitably exploit the 
expressivity of richer abstract domains as well as precision 
of CDCL architecture. This is attributed to the intelligent decision
heuristics which exploits the high-level structure of the problem 
combined with stronger deductions and clause learning mechanism aided 
by the richer abstract domains.

>>>>

\section{Contributions}
In this paper, we have the following contributions.
\begin{enumerate}
\item We present a procedure for lifting CDCL algorithm to 
relational and non-relational numerical abstract domain.  
To this end, we instatiate model search and conflict analysis 
phases of CDCL algorithm over intervals and octagon abstract 
domains.  We implement our own template-based numerical 
domains that supports complementation property, essential for 
such lifting.  To the best of our knowledge, this is the first 
instantiation of CDCL algorithm with relational abstract domains.

\item We present a new program analysis tool, {\em Titlis}, that 
is a strict generalisation of propositional CDCL algorithm.  From 
abstract interpretation perspective, {\em Titlis} uses decision 
and learning to improve the precision of abstract transformers.  
Thus, {\em Titlis} combines the efficiency of abstract domains 
while being path-sensitive and bit-precise at the same time.

\item  Experiments on several numerical and control-intensive benchmarks 
shows that the proposed generalization of CDCL algorithm is able to 
suitably exploit the expressivity of richer abstract domains as well 
as precision of CDCL architecture.  This is attributed to the 
intelligent decision heuristics which exploits the high-level 
structure of the problem combined with stronger deductions and 
clause learning mechanism aided by the richer abstract domains.
\end{enumerate}

### 2016-10-07 decision.tex
paper update
literals
decision

\section{Decision Heuristics}\label{decision}
Berkmin, longest-range, random, ordered, octagons

>>>>

\section{Decision}
A decision $\mathcal{D}$ is a meet irreducible that refines the 
current partial assignment.  A decision can be of the form 
$\langle x \preceq c \rangle$ or $\langle x \succeq c \rangle$, 
where $c$ is the bound and $x$ is a program variable.  A 
decision $\mathcal{D}$ must always be consistent with respect 
to the trail $\mathcal{T}$, that is, it must not contradict with 
the elements in the trail.  Each variable in propositional CDCL 
is assigned at most once at a particular decision level.  However, 
a variable can be assigned several times in our lifting of CDCL to 
numerical domains, each time with increasingly precise bounds.

Let $\mathcal{V}$ be a set of all singletons and non-singletons 
variables.  A singleton variable is one that has been assigned a 
singleton value, for example, $\langle x:[1,1] \rangle$.  Otherwise, 
the variable is non-singleton.  Given a set of variables $\mathcal{V}$, 
a decision phase heuristically chooses a non-singleton branching 
variable $v \in \mathcal{V}$, a bound $c$, and the polarity ($\succeq$ or 
$\preceq$).

We implemented several decision heuristics namely, {\em Berkmin}~\cite{}, 
{\em longest-range}, {\em ordered}, {\em random}.  The {\em ordered} 
decision heuristics creates an ordering among non-singleton variables, 
making decision on conditional variables (variables that appear in 
conditional branches) first before choosing numerical variables.  Thus, 
this heuristics is path-sensitive which gives significant speed-up for 
control-intensive benchmarks.
